Article counts per year figure

### 2022-01-31 article-counts-per-year-figure.Rmd
magrittr to replace dplyr

```{r}
library(dplyr)
dat <- readxl::read_xlsx(path = "data/publication-counts.xlsx", sheet = "counts")
dat %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = mrcount)) + ggplot2::geom_bar(stat = "identity")
```

>>>>

```{r}
library(magrittr)
dat <- readxl::read_xlsx(path = "data/publication-counts.xlsx", sheet = "counts")
dat %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = mrcount)) + ggplot2::geom_bar(stat = "identity")
```
